---
title: "mrm_stick_mult_qual"
author: "kira delmore"
date: "Sept 24, 2018"
output: 
  html_document: 
    keep_md: yes
---

#### load libs and data
```{r, message=F, warning=F}
library(tidyverse)
library(ecodist)
```

#### loop code from mrm_stick_qual.Rmd
#### you probably don't want to run this yourself so ive commented it out
```{r message=FALSE}
# results <- NA
# for (i in 1:1000){

#   #### load data
#   cor.tidy <- read_csv("C:/Users/Kira/Desktop/stickleback/cor_out3b_continuous_distance.csv")
# 
#   #### pairs
#   
#   boot <- c("boot_stream","boot_lake")
#   constance <- c("constance_stream","constance_lake")
#   geneva <- c("geneva_stream","geneva_lake")
#   joes <- c("joes_stream","joes_lake")
#   lq <- c("lq_benthic","lq_limnetic")
#   misty <- c("misty_stream","misty_lake")
#   pax <- c("pax_benthic","pax_limnetic")
#   pri <- c("pri_benthic","pri_limnetic")
#   roberts <- c("roberts_stream","roberts_lake")
#   
#   #### randomly select one from each
#   
#   random_boot <- sample(boot,1)
#   random_constance <- sample(constance,1)
#   random_geneva <- sample(geneva,1)
#   random_joes <- sample(joes,1)
#   random_lq <- sample(lq,1)
#   random_misty <- sample(misty,1)
#   random_pax <- sample(pax,1)
#   random_pri <- sample(pri,1)
#   random_roberts <- sample(roberts,1)
#   
#   #### subset dataset based on random selections
#   
#   cor.tidy <- cor.tidy[!grepl(random_boot, cor.tidy$pop_comp),]
#   cor.tidy <- cor.tidy[!grepl(random_constance, cor.tidy$pop_comp),]
#   cor.tidy <- cor.tidy[!grepl(random_geneva, cor.tidy$pop_comp),]
#   cor.tidy <- cor.tidy[!grepl(random_joes, cor.tidy$pop_comp),]
#   cor.tidy <- cor.tidy[!grepl(random_lq, cor.tidy$pop_comp),]
#   cor.tidy <- cor.tidy[!grepl(random_misty, cor.tidy$pop_comp),]
#   cor.tidy <- cor.tidy[!grepl(random_pax, cor.tidy$pop_comp),]
#   cor.tidy <- cor.tidy[!grepl(random_pri, cor.tidy$pop_comp),]
#   cor.tidy <- cor.tidy[!grepl(random_roberts, cor.tidy$pop_comp),]
#   
# #### get fst matrix together
# #### gregs loop
# 
# pops <- sort(unique(cor.tidy$pop2))
# 
# fst <- matrix(nrow = length(pops),ncol=length(pops))
# for (i in 1:length(pops)){
#   for (j in 1:length(pops)){
#     
#     tmp<- cor.tidy %>% filter(pop1 == pops[i], pop2 == pops[j]) %>% select(Correlation) %>% .$Correlation
#     if (length(tmp) == 1){
#       fst[i,j] <- tmp
#     }
#     
#   }
# }

# ## have to flip this matrix
# ## i dont know why I can't figure this out more elegantly
# fst <- apply(fst, 2, rev)
# fst <- t(apply(fst, 2, rev))
# fst <- as.dist(fst)
# 
# #### get ecology matrix together
# cor.tidy$Qual_ecology_score <- ordered(cor.tidy$Qual_ecology_score,levels=c("3","2","1","0"))
# pops <- sort(unique(cor.tidy$pop2))
# 
# ecology <- matrix(nrow = length(pops),ncol=length(pops))
# for (i in 1:length(pops)){
#   for (j in 1:length(pops)){
#     
#     tmp<- cor.tidy %>% filter(pop1 == pops[i], pop2 == pops[j]) %>% select(Qual_ecology_score) %>% .$Qual_ecology_score
#     if (length(tmp) == 1){
#       ecology[i,j] <- tmp
#     }
#     
#   }
# }
# 
# ecology <- apply(ecology, 2, rev)
# ecology <- t(apply(ecology, 2, rev))
# ecology <- as.dist(ecology)

# #### get euc matrix together
# 
# cor.tidy$euc.distance <- as.numeric(cor.tidy$euc.distance)
# 
# pops <- sort(unique(cor.tidy$pop2))
# 
# euc <- matrix(nrow = length(pops),ncol=length(pops))
# for (i in 1:length(pops)){
#   for (j in 1:length(pops)){
#     
#     tmp<- cor.tidy %>% filter(pop1 == pops[i], pop2 == pops[j]) %>% select(euc.distance) %>% .$euc.distance
#     if (length(tmp) == 1){
#       euc[i,j] <- tmp
#     }
#     
#   }
# }
# 
# euc <- apply(euc, 2, rev)
# euc <- t(apply(euc, 2, rev))
# euc <- as.dist(euc)

# #### run MRM
# z <- MRM(fst~ecology+euc,nperm = 10000)
# model_r <- z$r.squared[1]
# model_p <- z$r.squared[2]
# coef_ecol <- z$coef[2,1]
# coef_geog <- z$coef[3,1]
# p_ecol <- z$coef[2,2]
# p_geog <- z$coef[3,2]
# results_sample <- cbind(model_r,model_p,coef_ecol,coef_geog,p_ecol,p_geog)
# results <- rbind(results,results_sample)
# 
# }
# results <- results[-1,]
```

#### so now we have a df with results for 1000 random selection of a pop from each pair
```{r}
load("C:/Users/Kira/Desktop/stickleback/results_qual.R")
head(results)
```

#### i dont really know how we want to report these results
#### summarized below (my mind can't calculate CI for columns right now, feel free to add)
#### count of replicates where ecology was sign and geog was sign
```{r}
summary(results[,1:ncol(results)])
nrow(results[results[, "p_ecol"] <= 0.05,])
nrow(results[results[, "p_geog"] <= 0.05,])
```