---
title: "mrm_stick"
author: "kira delmore"
date: "may 5, 2018"
output: 
  html_document: 
    keep_md: yes
---

#### load libs and data
```{r, message=F, warning=F}
library(tidyverse)
library(ecodist)
cor.tidy <- read_csv("C:/Users/Kira/Desktop/stickleback/cor_out3b.csv")
```

#### randomly sample one population from those in same watershed
#### means that we go from having 23 comparisons to 14 in matrix format
#### random.org to randomly sample 1 of each pair (yup, that's how i did it)
```{r}
# boot	stream
# constance	lake
# geneva	lake
# joes	stream
# lq	benthic
# misty	lake
# pax	limnetic
# pri	benthic
# roberts	lake
nrow(cor.tidy)
cor.tidy <- cor.tidy[!grepl("boot_stream", cor.tidy$pop_comp),]
cor.tidy <- cor.tidy[!grepl("constance_lake", cor.tidy$pop_comp),]
cor.tidy <- cor.tidy[!grepl("geneva_lake", cor.tidy$pop_comp),]
cor.tidy <- cor.tidy[!grepl("joes_stream", cor.tidy$pop_comp),]
cor.tidy <- cor.tidy[!grepl("lq_benthic", cor.tidy$pop_comp),]
cor.tidy <- cor.tidy[!grepl("misty_lake", cor.tidy$pop_comp),]
cor.tidy <- cor.tidy[!grepl("pax_limnetic", cor.tidy$pop_comp),]
cor.tidy <- cor.tidy[!grepl("pri_benthic", cor.tidy$pop_comp),]
cor.tidy <- cor.tidy[!grepl("roberts_lake", cor.tidy$pop_comp),]
nrow(cor.tidy)
```

#### get fst matrix together
#### gregs loop
```{r}
pops <- sort(unique(cor.tidy$pop2))

fst <- matrix(nrow = length(pops),ncol=length(pops))
for (i in 1:length(pops)){
  for (j in 1:length(pops)){
    
    tmp<- cor.tidy %>% filter(pop1 == pops[i], pop2 == pops[j]) %>% select(Correlation) %>% .$Correlation
    if (length(tmp) == 1){
      fst[i,j] <- tmp
    }

  }
}

## have to flip this matrix
## i dont know why I can't figure this out more elegantly
fst <- apply(fst, 2, rev)
fst <- t(apply(fst, 2, rev))
fst <- as.dist(fst)
```

#### get ecology matrix together
#### binomial for now because im not sure where the qualitative variable is 
#### there are two variables it could be but both have four categories and i think should only have 3
```{r}
unique(cor.tidy$Ecology)
cor.tidy$Ecology <- gsub("Same_Ecology","0",cor.tidy$Ecology)
cor.tidy$Ecology <- gsub("Diff_Ecology","1",cor.tidy$Ecology)
unique(cor.tidy$Ecology)

pops <- sort(unique(cor.tidy$pop2))

ecology <- matrix(nrow = length(pops),ncol=length(pops))
for (i in 1:length(pops)){
  for (j in 1:length(pops)){
    
    tmp<- cor.tidy %>% filter(pop1 == pops[i], pop2 == pops[j]) %>% select(Ecology) %>% .$Ecology
    if (length(tmp) == 1){
      ecology[i,j] <- tmp
    }
    
  }
}

ecology <- apply(ecology, 2, rev)
ecology <- t(apply(ecology, 2, rev))
ecology <- as.dist(ecology)
```

#### get geography matrix together
#### binomial for now because im not sure where the qualitative variable is 
```{r}
unique(cor.tidy$Geography)
cor.tidy$Geography <- gsub("Same_Ocean","0",cor.tidy$Geography)
cor.tidy$Geography <- gsub("Diff_Ocean","1",cor.tidy$Geography)
unique(cor.tidy$Geography)

pops <- sort(unique(cor.tidy$pop2))

geography <- matrix(nrow = length(pops),ncol=length(pops))
for (i in 1:length(pops)){
  for (j in 1:length(pops)){
    
    tmp<- cor.tidy %>% filter(pop1 == pops[i], pop2 == pops[j]) %>% select(Geography) %>% .$Geography
    if (length(tmp) == 1){
      geography[i,j] <- tmp
    }
    
  }
}

geography <- apply(geography, 2, rev)
geography <- t(apply(geography, 2, rev))
geography <- as.dist(geography)
```

### check out the data
```{r}
plot(fst,ecology)
plot(fst,geography)
```

#### run MRM
#### interpretation of result = both ecology and geography explain sign variation in pairwise fst
#### based on para estimates geog more impt (also if i run a simple mantel test with just fst and ecol the corr is not sign)
```{r}
MRM(fst~ecology+geography,nperm = 10000)
```

### simple mantel tests
```{r}
library(biotools)
mantelTest(fst,ecology,alternative="two.sided")
mantelTest(fst,geography,alternative="two.sided")
```
